\section{Functional Requirements}
The following are the primary functional requirements of the FormalNet system:

\begin{enumerate}[label=FR\arabic*.]
  \item The system shall allow users to input an informal English sentence.
  \item The system shall send the input sentence to the backend API for formalization.
  \item The system shall return and display the formalized output to the user.
  \item The system shall allow registered users to log in and log out securely.
  \item The system shall store input-output history for logged-in users.
  \item The system shall allow users to edit and re-submit previously entered prompts.
  \item The system shall provide an admin panel for managing users and prompts.
\end{enumerate}


\section{Non-Functional Requirements}

These are constraints on how the system performs:

\begin{enumerate}[label=NFR\arabic*.]
  \item The system shall respond to input within 3 seconds under normal load.
  \item The backend shall be able to handle at least 10 concurrent users.
  \item The system shall be compatible with modern web browsers (Chrome, Firefox, Edge).
  \item The system shall maintain user data securely using hashed passwords.
  \item The model inference shall run on GPU if available, otherwise fallback to CPU.
  \item The application shall be deployed using a containerized architecture (e.g., Docker).
\end{enumerate}


\section{External Interface Requirements}

\subsection{User Interface}
\begin{itemize}
  \item The main page shall include a form to input informal text and display the formal output.
  \item The profile page shall show prompt history with options to edit or delete.
  \item The login/register pages shall include standard form fields with validation.
\end{itemize}

\subsection{API Interface}
\begin{itemize}
  \item The Django app shall send a POST request to the FastAPI backend at \texttt{/predict} with JSON input.
  \item The backend shall respond with JSON containing the formalized text.
  \item API must return HTTP status codes for error handling (e.g., 200 OK, 400 Bad Request).
\end{itemize}


